On the properties of discs around accreting brown dwarfs

### 2010-07-15 BDD_submit/paper.tex
Changed figures to .pdf and website url
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2379 25464f21-6099-402c-b30a-640f1d40d38b

The complete model grid, with derived photometry and isochrones, is
available online through our browsing
tool\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore
  disc} which is described in Appendix \ref{website}.

@@

\begin{figure}
  \includegraphics[scale=0.3,angle=90]{./Fig/albedo.ps}
 \caption{Figures of the albedo (top panel), and scattering
   (dashed line) and absorption (solid line) opacities (bottom
     panel) against log($\lambda$) (in $\mu$m) for our adopted dust
   population. For both panels the vertical dashed line is
   plotted at 10\,$\mu$m to highlight the silicate features.
   \label{albedo}}
\end{figure}

@@

Many observational studies use non-spectroscopic data to derive the
pertinent parameters. Therefore in order to examine the practical
effects in the `observational plane' we have used the SEDs to produce
broadband photometric magnitudes and subsequently colours. Broadband
magnitudes were also derived in a large range of other filter sets not
used explicitly in the analysis within this paper. These magnitudes
are available
online\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore
  disc} and are briefly discussed in Appendix \ref{website}. In
addition, monochromatic fluxes have been derived for all filters, and
again are available online and discussed in Appendix \ref{website}.

@@

\begin{figure*}
\begin{center}
  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/flare_-12_183.ps}\label{flare_-12_183}}
  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/flare_-7_193.ps}\label{flare_-7_193}}
\end{center}
 \caption{Figure showing the density structure ($\log \rho$) of the
   BDD system with $M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5, areal
   coverage=10\% and accretion rate of (a) \logmdot=$-12$ and (b) \logmdot = $-7$.}
\end{figure*}

@@

\begin{figure*}
\includegraphics[scale=0.5,angle=90]{./Fig/inner_temp.ps}
\caption{Figure showing data for the inner edge location ($R_{\rm
    inner}$, $R_*$). The typical accretors are shown in the left panel
  and the extreme accretors in the right panel (see text for
  explanation). Both panels separate the systems by period, with those
  systems with rotation periods of 0.5 and 5 days shown as red and
  blue symbols respectively. In addition, systems where $\Delta R_{\rm
    inner} < 1R_*$ are plotted as crosses and $\Delta R_{\rm inner} >
  1R_*$ as filled circles (this is only achieved by some systems
  classed as extreme accretors).\label{inner_temp}}
\end{figure*}

@@

\begin{figure*}
  \centering
  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/no_sub_183_density.ps}\label{no_sub_183_a}}
  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/no_sub_183_temp.ps}\label{no_sub_183_b}}
  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/sub_179_density.ps}\label{sub_179_a}}
  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/sub_179_temp.ps}\label{sub_179_b}}
  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/sub_181_density.ps}\label{sub_181_a}}
  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/sub_181_temp.ps}\label{sub_181_b}}

@@

\begin{figure*}
\includegraphics[scale=0.6,angle=90]{./Fig/acc_dom.ps}
\caption{Figure showing the photospheric flux (log(ergs$\rm{/s/cm}^2/{\rm
    \AA}$)) against $\lambda$ (log($\mu$m)) of a BD with
  $M=$0.04$M_{\odot}$, at 1 Myr. No disc is included, but blackbody
  fluxes from an accretion stream at the rates of \logmdot $=-8$, $-9$
  and $-12$ are shown as blue, black and red lines respectively. The
  bottom panels show accretion for a star rotating at 5 days, with the
  top panels showing that of 0.5 days. The left panels systems with an
  areal coverage of 10\% and the right panels has 1\%. The vertical
  and horizontal dashed lines (in the lower panels) denote the
  approximate sensitivity ranges of our chosen $V$, $I$, $J$ and $K$
  filters.\label{acc_dom}}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/flare_inc.ps}
  \caption{Figure showing both total SEDs of the systems shown in
    Figure \ref{flare_-12_183} and \ref{flare_-7_193} as the top and
    bottom panels respectively. The lines show the SEDs of all
    inclinations (see Table \ref{par_space_table}), with the
    obscuration angle shown as a dashed line, 71$^{\circ}$ and
    56$^{\circ}$ for \logmdot = $-$12 and $-$7
    respectively.\label{flare_inc}}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/flare_mag.ps}
  \caption{Figure showing $M_V$ and $M_J$ magnitudes as a function of
    inclination, shown as top, middle and lower panels
    respectively. The magnitudes of systems with $M_*=0.04M_{\odot}$,
    an age of 1 Myr, areal coverage of 10\% and rotation rate of 0.5
    days are shown as solid lines (and crosses). The systems with
    accretion rates of \logmdot = $-$12, $-$9 and $-$7, are shown in
    black, red and blue respectively. The panels also show the systems
    with the highest accretion rate but for a rotation rate of 5 days,
    as dashed lines (and crosses). The vertical dotted lines show the
    inclinations of 71$^{\circ}$ and 56$^{\circ}$. Finally, the inset
    panel simply shows a magnification of the region of interested for
    the $M_J$ magnitude. \label{flare_mag}}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/age_mass_VVI.ps}
  \caption{Figure showing CMDs in $M_V$, $(V-I)_0$ for typical
    accretors (\logmdot $\leq$ $-$9) in the left panels, and extreme
    accretors (\logmdot $>-9$) in the right panels. The black dashed
    and solid lines correspond to naked BD isochrones (from our grid)
    with \logmdot\ $-$9 and $-$12 for the left panels (typical
    accretors) and -9 and -6 in the right panels (extreme
    accretors). The rotation rates and areal coverages are set at 5
    days and 10\% respectively (changing these has little effect). The
    top panels also include as a solid green line the 1 Myr pre-MS
    isochrone of \citet{siess_2000} adjusted to a distance modulus of
    7 and an extinction of $A_V=2$, simulating a reddened background
    population. The top panels then separate the systems by accretion
    rate with \logmdot = $-$9, $-$10 and $-$11 \& $-$12 in the top left panel,
    and \logmdot = $-$6, $-$7 and $-$8 in the top right panel, shown blue,
    black and red dots respectively for both cases. The lower panels
    then split the systems into groups by inclination, with $\theta
    \leq$ 48$^{\circ}$, $\theta \geq$ 77$^{\circ}$ and $\theta=$ 56,
    64 \& 71$^{\circ}$, plotted as blue, red and black dots
    respectively.\label{age_mass_VVI}}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/age_mass_JJK.ps}
  \caption{Figure showing the same data in the same format and with
    the same symbol meanings as Figure \ref{age_mass_VVI}, but for
    $M_J$ and $(J-K)_0$ CMDs. However, for this Figure the \logmdot =
    $-$6 isochrone is not shown (lies significantly blueward of locus
    of data), and the pre-MS isochrone of \citet{siess_2000}, has been
    smoothed.\label{age_mass_JJK}}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/disc_frac_JHJK.ps}
  \caption{Figure showing $(J-K)_0$, $(J-H)_0$ CoCoDs for typical
    (left panel) and extreme accreting (right panels) systems. The top
    panels then separate the accretion rates with \logmdot = $-$9,
    $-$10 and $-$11 \& $-$12, and \logmdot = $-$6, $-$7 \& $-$8 shown
    as blue, black and red dots respectively for the typical (top left
    panel) and extreme (top right panel) accretors. The bottom panels
    then show the systems with the inclinations $\theta \leq
    48^{\circ}$ as blue dots, $\theta> 56$ \& $64^{\circ}$ as black
    dots and $\theta \geq 71^{\circ}$ as red
    dots.\label{disc_frac_JHJK}}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/disc_frac_irac.ps}
  \caption{Figure showing $([3.6]-[4.5])_0$, $([4.5]-[5.8])_0$ CoCoDs
    of both typical (left panels) and extreme (right panels)
    accretors. The panels separate the different accretion rates and
    inclinations as in Figure
    \ref{disc_frac_JHJK}.\label{disc_frac_irac}}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/disc_frac_mips.ps}
  \caption{Figure showing $(24-70)_0$, $(70-160)_0$ CoCoDs in the same
    format as Figure \ref{disc_frac_JHJK}. The smaller inset panels in
    the top panels show the separation between the naked (blue
    crosses) and BDD systems (red dots).\label{disc_frac_mips}}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[scale=0.65,angle=90]{./Fig/disc_cuts.ps}
  \caption{Figure showing both from top to bottom, the disc candidate
    selection of \citet{luhman_2005b}, \citet{luhman_2008},
    \citet{monin_2010} \citep[using the criteria of][]{gutermuth_2008}
    and \citet{kennedy_2009}. The photometry or $\alpha$ values for
    all models are shown, with naked stars as black crosses, 1 Myr BDD
    systems as blue dots and 10 Myr BDD systems as red dots. The
    dashed horizontal and vertical lines are disc selections from the
    studies in question. The left panels are the typical accretors and
    the right panels the extreme accretors. The top three panels are
    IRAC CoCoDs and the bottom panel plots the $\alpha$ value against
    run number (an arbitrary number).\label{disc_cuts}}
\end{figure*}

@@

As stated throughout this paper the data presented are available from
a web page\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore disc}.

>>>>

The complete model grid, with derived photometry and isochrones, is
available online through our browsing
tool\footnote{http://bd-server.astro.ex.ac.uk/} which is described in Appendix \ref{website}.

@@

\begin{figure}
  \includegraphics[scale=0.3,angle=90]{./Fig/albedo.pdf}
 \caption{Figures of the albedo (top panel), and scattering
   (dashed line) and absorption (solid line) opacities (bottom
     panel) against log($\lambda$) (in $\mu$m) for our adopted dust
   population. For both panels the vertical dashed line is
   plotted at 10\,$\mu$m to highlight the silicate features.
   \label{albedo}}
\end{figure}

@@

Many observational studies use non-spectroscopic data to derive the
pertinent parameters. Therefore in order to examine the practical
effects in the `observational plane' we have used the SEDs to produce
broadband photometric magnitudes and subsequently colours. Broadband
magnitudes were also derived in a large range of other filter sets not
used explicitly in the analysis within this paper. These magnitudes
are available online\footnote{http://bd-server.astro.ex.ac.uk/} and
are briefly discussed in Appendix \ref{website}. In addition,
monochromatic fluxes have been derived for all filters, and again are
available online and discussed in Appendix \ref{website}.

@@

\begin{figure*}
\begin{center}
  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/flare_-12_183.pdf}\label{flare_-12_183}}
  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/flare_-7_193.pdf}\label{flare_-7_193}}
\end{center}
 \caption{Figure showing the density structure ($\log \rho$) of the
   BDD system with $M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5, areal
   coverage=10\% and accretion rate of (a) \logmdot=$-12$ and (b) \logmdot = $-7$.}
\end{figure*}

@@

\begin{figure*}
\includegraphics[scale=0.5,angle=90]{./Fig/inner_temp.pdf}
\caption{Figure showing data for the inner edge location ($R_{\rm
    inner}$, $R_*$). The typical accretors are shown in the left panel
  and the extreme accretors in the right panel (see text for
  explanation). Both panels separate the systems by period, with those
  systems with rotation periods of 0.5 and 5 days shown as red and
  blue symbols respectively. In addition, systems where $\Delta R_{\rm
    inner} < 1R_*$ are plotted as crosses and $\Delta R_{\rm inner} >
  1R_*$ as filled circles (this is only achieved by some systems
  classed as extreme accretors).\label{inner_temp}}
\end{figure*}

@@

\begin{figure*}
  \centering
  \subfigure[]{\includegraphics[scale=0.27,angle=0]{./Fig/no_sub_183_density.pdf}\label{no_sub_183_a}}
  \subfigure[]{\includegraphics[scale=0.27,angle=0]{./Fig/no_sub_183_temp.pdf}\label{no_sub_183_b}}
  \subfigure[]{\includegraphics[scale=0.27,angle=0]{./Fig/sub_179_density.pdf}\label{sub_179_a}}
  \subfigure[]{\includegraphics[scale=0.27,angle=0]{./Fig/sub_179_temp.pdf}\label{sub_179_b}}
  \subfigure[]{\includegraphics[scale=0.27,angle=0]{./Fig/sub_181_density.pdf}\label{sub_181_a}}
  \subfigure[]{\includegraphics[scale=0.27,angle=0]{./Fig/sub_181_temp.pdf}\label{sub_181_b}}

@@

\begin{figure*}
\includegraphics[scale=0.6,angle=90]{./Fig/acc_dom.pdf}
\caption{Figure showing the photospheric flux (log(ergs$\rm{/s/cm}^2/{\rm
    \AA}$)) against $\lambda$ (log($\mu$m)) of a BD with
  $M=$0.04$M_{\odot}$, at 1 Myr. No disc is included, but blackbody
  fluxes from an accretion stream at the rates of \logmdot $=-8$, $-9$
  and $-12$ are shown as blue, black and red lines respectively. The
  bottom panels show accretion for a star rotating at 5 days, with the
  top panels showing that of 0.5 days. The left panels systems with an
  areal coverage of 10\% and the right panels has 1\%. The vertical
  and horizontal dashed lines (in the lower panels) denote the
  approximate sensitivity ranges of our chosen $V$, $I$, $J$ and $K$
  filters.\label{acc_dom}}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/flare_inc.pdf}
  \caption{Figure showing both total SEDs of the systems shown in
    Figure \ref{flare_-12_183} and \ref{flare_-7_193} as the top and
    bottom panels respectively. The lines show the SEDs of all
    inclinations (see Table \ref{par_space_table}), with the
    obscuration angle shown as a dashed line, 71$^{\circ}$ and
    56$^{\circ}$ for \logmdot = $-$12 and $-$7
    respectively.\label{flare_inc}}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/flare_mag.pdf}
  \caption{Figure showing $M_V$ and $M_J$ magnitudes as a function of
    inclination, shown as top, middle and lower panels
    respectively. The magnitudes of systems with $M_*=0.04M_{\odot}$,
    an age of 1 Myr, areal coverage of 10\% and rotation rate of 0.5
    days are shown as solid lines (and crosses). The systems with
    accretion rates of \logmdot = $-$12, $-$9 and $-$7, are shown in
    black, red and blue respectively. The panels also show the systems
    with the highest accretion rate but for a rotation rate of 5 days,
    as dashed lines (and crosses). The vertical dotted lines show the
    inclinations of 71$^{\circ}$ and 56$^{\circ}$. Finally, the inset
    panel simply shows a magnification of the region of interested for
    the $M_J$ magnitude. \label{flare_mag}}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/age_mass_VVI.pdf}
  \caption{Figure showing CMDs in $M_V$, $(V-I)_0$ for typical
    accretors (\logmdot $\leq$ $-$9) in the left panels, and extreme
    accretors (\logmdot $>-9$) in the right panels. The black dashed
    and solid lines correspond to naked BD isochrones (from our grid)
    with \logmdot\ $-$9 and $-$12 for the left panels (typical
    accretors) and -9 and -6 in the right panels (extreme
    accretors). The rotation rates and areal coverages are set at 5
    days and 10\% respectively (changing these has little effect). The
    top panels also include as a solid green line the 1 Myr pre-MS
    isochrone of \citet{siess_2000} adjusted to a distance modulus of
    7 and an extinction of $A_V=2$, simulating a reddened background
    population. The top panels then separate the systems by accretion
    rate with \logmdot = $-$9, $-$10 and $-$11 \& $-$12 in the top left panel,
    and \logmdot = $-$6, $-$7 and $-$8 in the top right panel, shown blue,
    black and red dots respectively for both cases. The lower panels
    then split the systems into groups by inclination, with $\theta
    \leq$ 48$^{\circ}$, $\theta \geq$ 77$^{\circ}$ and $\theta=$ 56,
    64 \& 71$^{\circ}$, plotted as blue, red and black dots
    respectively.\label{age_mass_VVI}}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/age_mass_JJK.pdf}
  \caption{Figure showing the same data in the same format and with
    the same symbol meanings as Figure \ref{age_mass_VVI}, but for
    $M_J$ and $(J-K)_0$ CMDs. However, for this Figure the \logmdot =
    $-$6 isochrone is not shown (lies significantly blueward of locus
    of data), and the pre-MS isochrone of \citet{siess_2000}, has been
    smoothed.\label{age_mass_JJK}}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/disc_frac_JHJK.pdf}
  \caption{Figure showing $(J-K)_0$, $(J-H)_0$ CoCoDs for typical
    (left panel) and extreme accreting (right panels) systems. The top
    panels then separate the accretion rates with \logmdot = $-$9,
    $-$10 and $-$11 \& $-$12, and \logmdot = $-$6, $-$7 \& $-$8 shown
    as blue, black and red dots respectively for the typical (top left
    panel) and extreme (top right panel) accretors. The bottom panels
    then show the systems with the inclinations $\theta \leq
    48^{\circ}$ as blue dots, $\theta> 56$ \& $64^{\circ}$ as black
    dots and $\theta \geq 71^{\circ}$ as red
    dots.\label{disc_frac_JHJK}}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/disc_frac_irac.pdf}
  \caption{Figure showing $([3.6]-[4.5])_0$, $([4.5]-[5.8])_0$ CoCoDs
    of both typical (left panels) and extreme (right panels)
    accretors. The panels separate the different accretion rates and
    inclinations as in Figure
    \ref{disc_frac_JHJK}.\label{disc_frac_irac}}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/disc_frac_mips.pdf}
  \caption{Figure showing $(24-70)_0$, $(70-160)_0$ CoCoDs in the same
    format as Figure \ref{disc_frac_JHJK}. The smaller inset panels in
    the top panels show the separation between the naked (blue
    crosses) and BDD systems (red dots).\label{disc_frac_mips}}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[scale=0.65,angle=90]{./Fig/disc_cuts.pdf}
  \caption{Figure showing both from top to bottom, the disc candidate
    selection of \citet{luhman_2005b}, \citet{luhman_2008},
    \citet{monin_2010} \citep[using the criteria of][]{gutermuth_2008}
    and \citet{kennedy_2009}. The photometry or $\alpha$ values for
    all models are shown, with naked stars as black crosses, 1 Myr BDD
    systems as blue dots and 10 Myr BDD systems as red dots. The
    dashed horizontal and vertical lines are disc selections from the
    studies in question. The left panels are the typical accretors and
    the right panels the extreme accretors. The top three panels are
    IRAC CoCoDs and the bottom panel plots the $\alpha$ value against
    run number (an arbitrary number).\label{disc_cuts}}
\end{figure*}

@@

As stated throughout this paper the data presented are available from
a web page\footnote{http://bd-server.astro.ex.ac.uk/}.
